Carbonate chemistry at Ny-Ålesund

### 2023-03-01 awipev-CO2.Rmd
Pangaea dataset finalized

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb_insi_temp, pco2_calc_fb_insi_temp, at_calc, pHint_tot_sf) %>%
  dplyr::rename(`pressure [dbar]` = depth, #        hydrostatic pressure (profiler)
                `s_insitu [unit]` = sal_insitu_ctd, # salinity in situ (profiler)
                `s_fb [unit]` = sal_fb,             # salinity (FerryBox)
                `t_11m [°C]` = temp_insitu_11m,     # temperature in situ (static at 11 m)
                `t_ctd [°C]` = temp_insitu_ctd,     # temperature in situ (profiler)
                `t_fb [°C]` = temp_fb,              # temperature (FerryBox)
                `t_sf [°C]` = temp_sf,              # temperature SeaFET (profiler)
                `at [umol kg-1]` = at,              # total alkalinity in situ, discrete measurements
                `at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
                `ct [umol kg-1]` = ct,              # dissolved inotganic carbon in situ, discrete measurements
                `ph_discrete [total scale]` = ph_s_sf_temp_insi, # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
                #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
                `pco2 [uatm]` = pco2_fb_insi_temp,  # Partial pressure of CO2 (FerryBox)
                #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
                `pH_sensor [total scale]` = pHint_tot_sf, # pH in situ at in situ temperature (profiler)
                #`pH_dur [total scale]` = pH_dur,
                #`pH_calc [total scale]` = ph_calc_fb
                ) %>% 
  dplyr::mutate(across(starts_with("pressure"), ~ round(.x, digits = 2)),
                across(starts_with("s_"), ~ round(.x, digits = 2)),
                across(starts_with("t_"), ~ round(.x, digits = 2)),
                across(starts_with("ph"), ~ round(.x, digits = 3)),
                across(starts_with("at") | 
                         starts_with("ct") |
                         starts_with("pco2"), ~ round(.x, digits = 1)),
                )

saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity (static at 11 m) 
# t_11m = temperature in situ (static at 11 m)
# t_ctd = temperature in situ (profiler)
# t_fb = temperature (FerryBox)
# t_sf = temperature SeaFET (profiler)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature (profiler)
# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature (FerryBox)
# pco2 = pCO2 in Ferrybox expressed at in situ temperature (FerryBox)
# pco2_calc = pCO2 in the FerryBox calculated from discrete measurements of AT and CT and expressed at in situ temperature
# pH_sf = pH seaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
# ph_calc = pH at FerryBox temperature calculated from CT and AT in the FerryBox
```

>>>>

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_sf, temp_fb, pco2_fb_insi_temp, pHint_tot_sf, at, ct, ph_s_sf_temp_insi) %>%
  dplyr::rename(`pressure [dbar]` = depth,          # hydrostatic pressure (profiler)
                `s_insitu [unit]` = sal_insitu_ctd, # salinity in situ (profiler)
                `s_fb [unit]` = sal_fb,             # salinity (FerryBox)
                `t_11m [°C]` = temp_insitu_11m,     # temperature in situ (static at 11 m)
                `t_ctd [°C]` = temp_insitu_ctd,     # temperature in situ (profiler)
                `t_fb [°C]` = temp_fb,              # temperature (FerryBox)
                `t_sf [°C]` = temp_sf,              # temperature SeaFET (profiler)
                `at [umol kg-1]` = at,              # total alkalinity in situ, discrete measurements
                #`at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
                `ct [umol kg-1]` = ct,              # dissolved inorganic carbon in situ, discrete measurements
                `ph_discrete [total scale]` = ph_s_sf_temp_insi, # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
                #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
                `pco2 [uatm]` = pco2_fb_insi_temp,  # partial pressure of CO2 (FerryBox)
                #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
                `pH_sensor [total scale]` = pHint_tot_sf, # pH in situ at in situ temperature (profiler)
                #`pH_dur [total scale]` = pH_dur,
                #`pH_calc [total scale]` = ph_calc_fb
                ) %>% 
  dplyr::mutate(across(starts_with("pressure"), ~ round(.x, digits = 2)),
                across(starts_with("s_"), ~ round(.x, digits = 2)),
                across(starts_with("t_"), ~ round(.x, digits = 2)),
                across(starts_with("ph"), ~ round(.x, digits = 3)),
                across(starts_with("at") | 
                         starts_with("ct") |
                         starts_with("pco2"), ~ round(.x, digits = 1)),
                )
# replace NaNs by NAs
pangaea <- pangaea %>% 
  mutate_all(~ifelse(is.nan(.), NA, .))

#saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
#write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
saveRDS(file= "data/AWIPEV-CO2_v1.rds", pangaea)
write_csv(pangaea, file = "data/AWIPEV-CO2_v1.csv")
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity (static at 11 m) 
# t_11m = temperature in situ (static at 11 m)
# t_ctd = temperature in situ (profiler)
# t_fb = temperature (FerryBox)
# t_sf = temperature SeaFET (profiler)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature (profiler)
# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature (FerryBox)
# pco2 = pCO2 in Ferrybox expressed at in situ temperature (FerryBox)
# pco2_calc = pCO2 in the FerryBox calculated from discrete measurements of AT and CT and expressed at in situ temperature
# pH_sf = pH seaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
# ph_calc = pH at FerryBox temperature calculated from CT and AT in the FerryBox
```
